---
title: "Main Analysis"
output: github_document
---

# Analysis code

```{r setup, include=F}
library(tidyverse)
library(stringr)
library(brms)
library(rstan)
library(gtools)
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(knitr)
library(lme4)
library(xtable)
```

Functions:

 - process_data - reads in data and does exclusions 
 - process_spr - reads in SPR data and does exclusions
 - for_model - relabels for word position, selects one type of sentence
 - brm_modelling - does actual modelling
 
```{r more_set_up}

process_data <- function(source){
  #source = .rds file location of data
  #returns tibble of data after participant removal, and with only correct answers
  data <- read_rds(source)
  data_filtered <- data %>% 
  filter(citizen=="yes" & native=="yes" & resident=="yes")

message("Removed ", format(100-100*nrow(data_filtered)/nrow(data), digits=2), "% participants who are not citizens, native speakers, or residents of the US.")

message("We have ", length(unique(data_filtered$subject)), " participants left.")

#filter out and adjust bad data points

#remove na points that participants didn't see
data_no_na<- data_filtered %>% 
  filter(!(is.na(rt)))
  

message("Removed ", format(100-100*nrow(data_no_na)/nrow(data_filtered), digits=2), "% of the data for being na (after a mistake).")

#remove mistakes
 data_cleaned <- data_no_na %>% 
   filter(correct=="yes") %>% 
   select(-correct)

message("Removed ", format(100-100*nrow(data_cleaned)/nrow(data_no_na), digits=2), "% of the data for not having correct answer.")

message(format(100*nrow(data_cleaned)/nrow(data_filtered), digits=2), "% of possible data is left" )
data_no_0 <-  data_cleaned %>% 
  filter(rt!=0)

message("Removed ", format(100-100*nrow(data_no_0)/nrow(data_cleaned), digits=2), "% of the data for having a RT of 0.")

data_no_0
}

process_spr <- function(source){
  #source = .rds file location of data
  #returns tibble of data after participant removal, and with only correct answers
  data <- read_rds(source)
  data_filtered <- data %>% 
  filter(citizen=="yes" & native=="yes" & resident=="yes") %>% 
    mutate(word_num=word_num-1)

message("Removed ", format(100-100*nrow(data_filtered)/nrow(data), digits=2), "% participants who are not citizens, native speakers, or residents of the US.")

message("We have ", length(unique(data_filtered$subject)), " participants left.")

data_accurate <- data_filtered %>% 
  filter(accuracy>.8)

message("Removed ", format(100-100*nrow(data_accurate)/nrow(data_filtered), digits=2), "% participants who did not get at least 80% of comprehension questions correct.")

message("We have ", length(unique(data_accurate$subject)), " participants left.")
#filter out and adjust bad data points

#remove na points that participants didn't see
data_no_na<- data_accurate %>% 
  filter(!(is.na(rt)))

message("Removed ", format(100-100*nrow(data_no_na)/nrow(data_accurate), digits=2), "% of the data for being na.")

data_no_0 <-  data_no_na %>% 
  filter(rt!=0)

message("Removed ", format(100-100*nrow(data_no_0)/nrow(data_no_na), digits=2), "% of the data for having a RT of 0.")

data_no_0
}

for_model <- function(data, type){
  #data is tibble of data (output of process_data), type is "rel", "adv", or "noun"

rel_labelled <- read_rds("../Labelled/rel_clause_labelled.rds")
adv_labelled <- read_rds("../Labelled/adv_clause_labelled.rds")
noun_labelled <- read_rds("../Labelled/noun_clause_labelled.rds")

if(type=="rel"){
data_rel <- data %>% 
  filter(type=="relative_high"| type=="relative_low") %>% 
  left_join(rel_labelled, by=c("word_num", "sentence", "type", "word", "group"="item_num")) %>% 
   mutate(item.factor=as.factor(group),
         type.numeric=ifelse(type=="relative_low", 0, 1)) #treatment code expected as 0, unusual as 1

return(data_rel)}

if(type=="adv"){
data_adv<- data %>% 
  filter(type=="adverb_high"|type=="adverb_low") %>% 
  left_join(adv_labelled, by=c("word_num", "sentence", "type", "word", "group"="item_num")) %>% 
  mutate(mod_word_number=ifelse(multi_word=="yes"&mod_word_number>0, mod_word_number-1, mod_word_number)) %>% 
  group_by(subject, group, mod_word_number, type) %>% 
  summarize(rt=mean(rt)) %>% 
  mutate(item.factor=as.factor(group),
         type.numeric=ifelse(type=="adverb_low", 0, 1)) #treatment code expected as 0, unusual as 1

return(data_adv)}
if(type=="noun"){
data_noun <- data%>% 
  filter(type=="and_no_comma"|type=="and_comma") %>% 
  left_join(noun_labelled, by=c("word_num", "sentence", "type", "word", "group"="item_num")) %>% 
   mutate(item.factor=as.factor(group),
         type.numeric=ifelse(type=="and_comma", 0, 1)) #treatment code expected as 0, unusual as 1

return(data_noun)
}

}

brm_modelling <- function(data){
  results <- tibble(mod_word_num=NA, mean=NA, low=NA, high=NA, above=NA, intercept=NA)
for (i in (-5:5)){
  data_test <- data %>% filter(mod_word_number==i)

system.time(model_test <- brm(log(rt) ~ type.numeric +(type.numeric|item.factor)+(type.numeric|subject), data_test))
fe <- fixef(model_test)
above <- mean(extract(model_test$fit, "b_type.numeric")[[1]]>0)
results <- add_row(results, "mod_word_num"=i, "mean"=fe[2], "low"=fe[6], "high"=fe[8], "above"=above, "intercept"=fe[1])
}
results_fixed <- results %>% mutate(pval_equiv = signif(2*pmin(above,1-above), digits=2)) %>% 
  filter(!is.na(mod_word_num)) %>% 
  mutate(mean_ms=exp(mean+intercept)-exp(intercept),
         low_ms=exp(low+intercept)-exp(intercept),
         high_ms=exp(high+intercept)-exp(intercept))

results_fixed
}

```

 Run analysis for relative clauses
 
```{r g_rel_plot, echo=F, cache=T, include=F}
rel_g <- process_data("../Data/Processed/g_maze.rds") %>% 
  for_model("rel")

rel_g_results <- brm_modelling(rel_g)


```

```{r l_rel_plot, echo=F, cache=T, include=F}
rel_l <- process_data("../Data/Processed/l_maze.rds") %>% 
  for_model("rel")

rel_l_results <- brm_modelling(rel_l)

```


```{r spr_rel_plot, echo=F, cache=T, include=F}
rel_spr <- process_spr("../Data/Processed/spr.rds") %>% 
  for_model("rel")

rel_spr_results <- brm_modelling(rel_spr)


```
```{r gulo_rel_plot, echo=F, cache=T, include=F}
rel_gulo <- process_data("../Data/Processed/gulo_maze.rds") %>% 
  for_model("rel")

rel_gulo_results <- brm_modelling(rel_gulo)


```
```{r one_b_rel_plot, echo=F, cache=T, include=F}
rel_one_b <- process_data("../Data/Processed/one_b_maze.rds") %>% 
  for_model("rel")

rel_one_b_results <- brm_modelling(rel_one_b)


```

Run analysis for adverbs

```{r g_adv_plot, echo=F, cache=T, include=F}
adv_g <- process_data("../Data/Processed/g_maze.rds") %>% 
  for_model("adv")

adv_g_results <- brm_modelling(adv_g)

```

```{r l_adv_plot, echo=F, cache=T, include=F}
adv_l <- process_data("../Data/Processed/l_maze.rds") %>% 
  for_model("adv")

adv_l_results <- brm_modelling(adv_l)

```

```{r spr_adv_plot, echo=F, cache=T, include=F}
adv_spr <- process_spr("../Data/Processed/spr.rds") %>% 
  for_model("adv")

adv_spr_results <- brm_modelling(adv_spr)


```

```{r gulo_adv_plot, echo=F, cache=T, include=F}
adv_gulo <- process_data("../Data/Processed/gulo_maze.rds") %>% 
  for_model("adv")

adv_gulo_results <- brm_modelling(adv_gulo)

```

```{r one_b_adv_plot, echo=F, cache=T, include=F}
adv_one_b <- process_data("../Data/Processed/one_b_maze.rds") %>% 
  for_model("adv")

adv_one_b_results <- brm_modelling(adv_one_b)

```

Run analysis for NP v S

```{r np_plot_g, echo=F, message=F, cache=T, include=F}

noun_g <- process_data("../Data/Processed/g_maze.rds") %>% 
  for_model("noun")

noun_g_results <- brm_modelling(noun_g)
```


```{r np_plot_l, echo=F, message=F, cache=T, include=F}

noun_l <- process_data("../Data/Processed/l_maze.rds") %>% 
  for_model("noun") 

noun_l_results <- brm_modelling(noun_l)


```

```{r np_plot_spr, echo=F, message=F, cache=T, include=F}

noun_spr <- process_spr("../Data/Processed/spr.rds") %>% 
  for_model("noun")

noun_spr_results <- brm_modelling(noun_spr)

```
```{r np_plot_gulo, echo=F, message=F, cache=T, include=F}

noun_gulo <- process_data("../Data/Processed/gulo_maze.rds") %>% 
  for_model("noun")

noun_gulo_results <- brm_modelling(noun_gulo)
```

```{r np_plot_one_b, echo=F, message=F, cache=T, include=F}

noun_one_b <- process_data("../Data/Processed/one_b_maze.rds") %>% 
  for_model("noun")

noun_one_b_results <- brm_modelling(noun_one_b)
```

Re-analyse Witzel data

```{r set_up_witzel, include=F}

g_lab <- read_rds("../Witzel/G_data.rds") %>%  filter(correct=="yes")

l_lab <- read_rds("../Witzel/L_data.rds") %>% filter(correct=="yes")

spr_lab <- read_rds("../Witzel/SPR_data.rds") %>%   filter(accuracy>.8)
```

```{r, include=F, cache=T}
rel_g_lab <- g_lab %>% 
  for_model("rel")

rel_g_lab_results <- brm_modelling(rel_g_lab)
```

```{r, include=F, cache=T}
rel_l_lab <- l_lab %>% 
  for_model("rel")

rel_l_lab_results <- brm_modelling(rel_l_lab)
```

```{r, include=F, cache=T}
rel_spr_lab <- spr_lab %>% 
  for_model("rel")

rel_spr_lab_results <- brm_modelling(rel_spr_lab)
```

```{r, include=F, cache=T}
adv_g_lab <- g_lab %>% 
  for_model("adv")

adv_g_lab_results <- brm_modelling(adv_g_lab)
```

```{r, include=F, cache=T}
adv_l_lab <- l_lab %>% 
  for_model("adv")

adv_l_lab_results <- brm_modelling(adv_l_lab)
```

```{r, include=F, cache=T}
adv_spr_lab <- spr_lab %>% 
  for_model("adv")

adv_spr_lab_results <- brm_modelling(adv_spr_lab)
```

```{r, include=F, cache=T}
noun_g_lab <- g_lab %>% 
  for_model("noun")

noun_g_lab_results <- brm_modelling(noun_g_lab)
```

```{r, include=F, cache=T}
noun_l_lab <- l_lab %>% 
  for_model("noun")

noun_l_lab_results <- brm_modelling(noun_l_lab)
```

```{r, include=F, cache=T}
noun_spr_lab <- spr_lab %>% 
  for_model("noun")

noun_spr_lab_results <- brm_modelling(noun_spr_lab)
```

# Graph for paper 

```{r prep}
rel_g_results <- rel_g_results %>% mutate(type="Web\nG-maze")
rel_l_results <- rel_l_results %>% mutate(type="Web\nL-maze")
rel_spr_results <- rel_spr_results %>% mutate(type="Web\nSPR")
rel_gulo_results <- rel_gulo_results %>% mutate(type="Web A-maze\nGulordava")
rel_one_b_results <- rel_one_b_results %>% mutate(type="Web A-maze\nJozefowicz")
rel_g_lab_results <- rel_g_lab_results %>% mutate(type="Lab\nG-maze")
rel_l_lab_results <- rel_l_lab_results %>% mutate(type="Lab\nL-maze")
rel_spr_lab_results <- rel_spr_lab_results %>% mutate(type="Lab\nSPR")
rel_all <- rel_g_results %>% union(rel_l_results) %>% union(rel_spr_results) %>%  union(rel_gulo_results) %>% union(rel_one_b_results) %>% union(rel_l_lab_results) %>% union(rel_g_lab_results) %>% union(rel_spr_lab_results) %>% mutate(topic="Relative")

adv_g_results <- adv_g_results %>% mutate(type="Web\nG-maze")
adv_l_results <- adv_l_results %>% mutate(type="Web\nL-maze")
adv_spr_results <- adv_spr_results %>% mutate(type="Web\nSPR")
adv_gulo_results <- adv_gulo_results %>% mutate(type="Web A-maze\nGulordava")
adv_one_b_results <- adv_one_b_results %>% mutate(type="Web A-maze\nJozefowicz")
adv_g_lab_results <- adv_g_lab_results %>% mutate(type="Lab\nG-maze")
adv_l_lab_results <- adv_l_lab_results %>% mutate(type="Lab\nL-maze")
adv_spr_lab_results <- adv_spr_lab_results %>% mutate(type="Lab\nSPR")
adv_all <- adv_g_results %>% union(adv_l_results) %>% union(adv_spr_results)%>% union(adv_gulo_results) %>% union(adv_one_b_results) %>%union(adv_l_lab_results) %>% union(adv_g_lab_results) %>% union(adv_spr_lab_results) %>%  mutate(topic="Adverb")

noun_g_results <- noun_g_results %>% mutate(type="Web\nG-maze")
noun_l_results <- noun_l_results %>% mutate(type="Web\nL-maze")
noun_spr_results <- noun_spr_results %>% mutate(type="Web\nSPR")
noun_gulo_results <- noun_gulo_results %>% mutate(type="Web A-maze\nGulordava")
noun_one_b_results <- noun_one_b_results %>% mutate(type="Web A-maze\nJozefowicz")
noun_g_lab_results <- noun_g_lab_results %>% mutate(type="Lab\nG-maze")
noun_l_lab_results <- noun_l_lab_results %>% mutate(type="Lab\nL-maze")
noun_spr_lab_results <- noun_spr_lab_results %>% mutate(type="Lab\nSPR")
noun_all <- noun_g_results %>% union(noun_l_results) %>% union(noun_spr_results)%>% union(noun_gulo_results) %>%  union(noun_one_b_results)%>%union(noun_l_lab_results) %>% union(noun_g_lab_results) %>% union(noun_spr_lab_results) %>% mutate(topic="S v NP")

all <- rel_all %>% union(adv_all) %>% union(noun_all) %>% mutate(type=factor(type, levels=c("Lab\nSPR","Lab\nL-maze", "Lab\nG-maze","Web\nSPR", "Web\nL-maze","Web\nG-maze", "Web A-maze\nGulordava", "Web A-maze\nJozefowicz" )),
                  topic=factor(topic, levels=c("Relative","Adverb", "S v NP"))) 

```

```{r stuff, fig.height=8, fig.width=7}
all2 <- all %>% filter(mod_word_num>-2) %>% filter(mod_word_num<5)
ggplot(all2)+
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  scale_x_continuous(limits = c(-.5,3.5), breaks=c(0,1,2,3), labels=c("0","1","2","3"))+
  geom_point(aes(x=mod_word_num, y=mean_ms, color=type))+
  geom_errorbar(aes(x=mod_word_num, ymin=low_ms, ymax=high_ms), direction="y", width=.2)+
  geom_line(aes(mod_word_num, mean_ms, color=type))+
 geom_text(aes(x=case_when(
   pval_equiv==0~ mod_word_num+.50,
   (mod_word_num==1 & type=="Web\nSPR") ~ mod_word_num-.25,
   (mod_word_num==2 & type=="Lab\nG-maze") ~ mod_word_num+.5,
   (mod_word_num==0 & type=="Web\nG-maze") ~ mod_word_num+.55,
   (mod_word_num==0 & topic=="Relative") ~ mod_word_num+.6,
   mod_word_num==0 ~ mod_word_num+.55, 
   mod_word_num==1 ~ mod_word_num+.4,
   TRUE ~ mod_word_num+.25),
   y=case_when(
     pval_equiv==0~ mean_ms+20,
     (mod_word_num==1 & type=="Lab\nG-maze")~mean_ms+100,
     (mod_word_num==2 & topic=="Relative")~mean_ms+150,
     TRUE ~ mean_ms+70)
   , label=case_when(
     (pval_equiv==0)&(mod_word_num>-1) ~"< 0.001",
    (pval_equiv<=.05)&(mod_word_num>-1) ~ as.character(signif(pval_equiv,2)),
     TRUE ~ ""
   )), size=4)+
  facet_grid(type~topic, scales="free_y", space="free_y")+
  coord_cartesian(xlim=c(0,3))+
  labs(title="Penalty for high attachment or no comma conditions", y="Difference in ms", x="Word position: 0=disambiguating word")+
  theme_bw()+geom_blank(aes(y=150))+geom_blank( aes(y=-50))+
  theme(legend.position="none", text = element_text(size = 12, colour="black"), panel.grid.minor.x = element_blank())+
  scale_y_continuous(breaks=c(-100, 0, 100, 200))+
  scale_color_manual(values=c("tan4", "springgreen4", "blue3", "tan2", "palegreen3", "skyblue3", "darkorchid2", "hotpink2"))


ggsave("../graph_for_cuny.pdf")
```




# Fuller results
For each word position, from -5 to 5 (disambiguating/critical word is 0). Estimated effect size in ms (of dispreferred - preferred). P-value equivalent given in parentheses. 

```{r}
table_data <- all %>% select(mean_ms, mod_word_num, type, topic, pval_equiv) %>%
  mutate(mean_ms=round(mean_ms), 
         pval_equiv=signif(pval_equiv, 2), 
         "Word\nPosition"=factor(mod_word_num, levels=c("-5","-4","-3","-2","-1","0","1","2","3","4","5")),
         combined=str_c(mean_ms, " (", pval_equiv, ")")) %>% select(-pval_equiv, -mean_ms, -mod_word_num) %>% spread(type, combined)

write_rds(all, "summ.rds")

table_rel <- table_data %>% filter(topic=="Relative") %>% select(-topic)
table_adv <- table_data %>% filter(topic=="Adverb") %>% select(-topic)

table_noun <- table_data %>% filter(topic=="S v NP") %>% select(-topic)
```

## Relative Clause Results
Relative clause attatchment: (always using reflexive pronouns)

  - The son of the actress who shot *herself* on the set was under investigation. (low attachment) versus
  - The son of the actress who shot *himself* on the set was under investigation. (high attatchment)

Here word position is measured off of where the reflexive it was. So 'herself' or 'himself' is 0, the following word is 1, the preceding word is -1 etc.

```{r}
kable(table_rel)
```

## Adverb Results 
Adverb attatchment: (always temporal adverbs)

 - Susan bought the wine she will drink *next week*, but she didn't buy any cheese. (low attachment) versus
 - Susan bought the wine she will drink *last week*, but she didn't buy any cheese. (high attachment)

Here word position is measured by  how many words after the temporal adjective it was. So 'last' 'next', 'week', and 'tomorrow' would all be 0, 'but' is 1 etc.

```{r}
kable(table_adv)
```

## S v NP conjunction Results
NP/S coordination: 

 - the robber shot the jeweler, and the salesman *reported* the crime to the police. (unambiguous due to comma) versus
 - the robber shot the jeweler and the salesman *reported* the crime to the police. (ambiguous)
 
Here position is sentence is measured relative to the second verb (disambiguation). So 'reported' is 0, 'the' is 1 etc.

```{r}
kable(table_noun)


```


